Finding Maximum $k$-Cliques Faster using Lazy Global Domination

### 2016-05-17 paper/paper.tex
Deanonymous

% \frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
% \pdfinfo{
% /Title (Finding Maximum $k$-Cliques Faster using Lazy Global Domination)
% /Author (Ciaran McCreesh, Patrick Prosser)}
\pdfinfo{
/Title (Finding Maximum $k$-Cliques Faster using Lazy Global Domination)
/Author (First Author and Second Author)}
\setcounter{secnumdepth}{0}

\begin{document}
\title{Finding Maximum $k$-Cliques Faster using Lazy Global Domination}
% \author{
%    Ciaran McCreesh%
%    \thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/K503058/1]}
%    \and
%    Patrick Prosser
%    \\ University of Glasgow, Glasgow, Scotland
%}
\author{
    First Author%
    \thanks{This work was supported by a pile of unmarked bills from an anonymous funding agency}
    \and
    Second Author
    \\ Secret Department of Secrecy, Some Institution, Somewhere
}
\maketitle

>>>>

% \frenchspacing
\setlength{\pdfpagewidth}{8.5in}
\setlength{\pdfpageheight}{11in}
\pdfinfo{
/Title (Finding Maximum $k$-Cliques Faster using Lazy Global Domination)
/Author (Ciaran McCreesh, Patrick Prosser)}
\setcounter{secnumdepth}{0}

\begin{document}
\title{Finding Maximum $k$-Cliques Faster using Lazy Global Domination}
 \author{
    Ciaran McCreesh%
    \thanks{This work was supported by the Engineering and Physical Sciences Research Council [grant number EP/K503058/1]}
    \and
    Patrick Prosser
    \\ University of Glasgow, Glasgow, Scotland
}
\maketitle
